---
title: "JuliaCall in R Markdown"
author: "Changcheng Li"
date: "`r Sys.Date()`"
output: 
  rmarkdown::github_document
---

## Use JuliaCall as Julia Engine in R Markdown

To use `JuliaCall` package for julia engine in R Markdown document.
Just set the engine for julia to `JuliaCall::eng_juliacall` like this:

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_engines$set(julia = JuliaCall::eng_juliacall)
```

Below is how it looks like when using `JuliaCall`
as language engine for Julia. 

## How Does JuliaCall in R Markdown Look Like?

```{julia, cache=TRUE}
## This is a julia language chunk.
## In julia, the command without ending semicolon will trigger the display
## so is JuliaCall package. 
## The julia display will follow immediately after the corresponding command
## just as the R code in R Markdown.
a = sqrt(2)
a = sqrt(2);

## And lots of different types of display are supported in JuliaCall.
## Like markdown and plots.
@doc sqrt
```

### Support for `Plots.jl`

`Plots.jl` is an easy to use and powerful julia package for plotting,
<https://github.com/JuliaPlots/Plots.jl>.
And `JuliaCall` supports `Plots.jl` of cource!!

```{julia, cache=TRUE}
using Plots
```

#### PyPlot backend

```{julia, cache=TRUE}
pyplot()
plot(Plots.fakedata(50,5),w=3)
```

#### GR backend

```{julia, cache=TRUE}
gr()
plot(Plots.fakedata(50,5),w=3)
```

## Get Access to Julia in R Chunk

And you can also get access to julia variables in R code chunk quite easily
using `JuliaCall`, for example:
```{r, cache=TRUE}
library(JuliaCall)
## This is a R language chunk.
## In the previous julia chunk, we define variable a, 
## we can use functions in JuliaCall to get access to it.
julia_eval("a")
```
