---
title: "JuliaCall in R Markdown"
author: "Changcheng Li"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document
---

<style>
.JuliaDisplay {
    color: blue;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How Does JuliaCall in R Markdown Look Like?

```{r, cache=TRUE}
library(JuliaCall)

julia_setup()

julia_command("sqrt(2)")

julia_command("@doc sqrt")

julia_library("Gadfly")

julia_command("Gadfly.plot(y = [1 2 3])")

julia_library("Plots")

julia_command("pyplot()")

julia_command("Plots.plot(Plots.fakedata(50,5),w=3)")

julia_command("Plots.plot(sin,(x->begin sin(2x) end),0,2pi,line=4,leg=false,fill=(0,:orange))")
```

## Limitations

Currently only R Markdown html output is fully supported by
`JuliaCall`, otherwise julia display like plots won't show in R Markdown document.

## Custom Style of Julia Display in R Markdown Using CSS

When using `JuliaCall` in R Markdown,
everything that displayed by julia will be wrapped in 
a div with `class = "JuliaDisplay"`,
so you could customize the looking of julia display very easily using css,
for example, I use

```
    <style>
    .JuliaDisplay {
        color: blue;
    }
    </style>
```

in this document.
