---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# JuliaCall for Seamless Integration of R and Julia

Package JuliaCall is an R interface to 'Julia',
which is a high-level, high-performance dynamic programming language
for numerical computing, see <https://julialang.org/> for more information.
    
[![Travis-CI Build Status](https://travis-ci.org/Non-Contradiction/JuliaCall.svg?branch=master)](https://travis-ci.org/Non-Contradiction/JuliaCall)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

You can get `JuliaCall` by
```{r eval=FALSE}
devtools::install_github("Non-Contradiction/JuliaCall")
```

## Basic Usage
```{r}
library(JuliaCall)

julia <- julia_setup()

julia$command("a = sqrt(2)"); julia$eval_string("a")

julia$eval_string("sqrt(2)")

julia$call("sqrt", 2)

julia$eval_string("sqrt")(2)

2 %>J% sqrt
```

## How to Get Help?

One way to get help is just using `julia$help` like the following example:

```{r}
julia$help("sqrt")

julia$help("sqrtm")
```

And you are more than welcome to contact me about `JuliaCall`
at <lch34677@gmail.com> or <cxl508@psu.edu>.

## JuliaCall for R Package Developers

If you are interested in developing an R package which is an interface for
a Julia package, `JuliaCall` is an ideal choice for that!

Basically you only need to find the Julia function or Julia module you want to have in `R`
and then just `using` the module and `call` the function.
An example is `ipoptjlr`, which can be found at <https://github.com/Non-Contradiction/ipoptjlr>.

If you have any issues in developing an `R` package using `JuliaCall`,
you may report it using the link: <https://github.com/Non-Contradiction/JuliaCall/issues/new>.
Or email me at <lch34677@gmail.com> or <cxl508@psu.edu>.

## Suggestion and Issue Reporting

`JuliaCall` is under active development now.
Any suggestion or issue reporting is welcome!
You may report it using the link: <https://github.com/Non-Contradiction/JuliaCall/issues/new>.
Or email me at <lch34677@gmail.com> or <cxl508@psu.edu>.

And if you encounter some issues which crash `R` or `RStudio`,
then you may have met segfault errors. 
I am very sorry.
And I am trying my best to remove errors like that.
It will be much appreciated if you can 

- download the source of `JuliaCall` from Github, 
- open `JuliaCall.Rproj` in your RStudio or open `R` from the directory where you download the source of `JuliaCall`,
- run `devtools::check()` to see the result of `R CMD check` for `JuliaCall` on your machine,
- and paste the result to the issue report.







