---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# JuliaCall for Seamless Integration of R and Julia

[![Travis-CI Build Status](https://travis-ci.org/Non-Contradiction/JuliaCall.svg?branch=master)](https://travis-ci.org/Non-Contradiction/JuliaCall)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/Non-Contradiction/JuliaCall?branch=master&svg=true)](https://ci.appveyor.com/project/Non-Contradiction/JuliaCall)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/JuliaCall)](https://cran.r-project.org/package=JuliaCall)

Package JuliaCall is an R interface to 'Julia',
which is a high-level, high-performance dynamic programming language
for numerical computing, see <https://julialang.org/> for more information.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

`JuliaCall` is on CRAN now! To use package `JuliaCall`, you first have to install `Julia`
<https://julialang.org/> on your computer, and then you can install `JuliaCall` just like
any other R packages by
```{r eval=FALSE}
install.packages("JuliaCall")
```

You can get the development version of `JuliaCall` by
```{r eval=FALSE}
devtools::install_github("Non-Contradiction/JuliaCall")
```

## Basic Usage
```{r}
library(JuliaCall)

## Do initial setup

julia <- julia_setup()

## Different ways for using Julia to calculate sqrt(2)

julia$command("a = sqrt(2)"); julia$eval_string("a")
julia_command("a = sqrt(2)"); julia_eval_string("a")

julia$eval_string("sqrt(2)")
julia_eval_string("sqrt(2)")

julia$call("sqrt", 2)
julia_call("sqrt", 2)

julia$eval_string("sqrt")(2)
julia_eval_string("sqrt")(2)

julia$assign("x", sqrt(2)); julia$eval_string("x")
julia_assign("x", sqrt(2)); julia_eval_string("x")

julia$assign("rsqrt", sqrt); julia$call("rsqrt", 2)
julia_assign("rsqrt", sqrt); julia_call("rsqrt", 2)

2 %>J% sqrt

## You can use `julia$exists` as `exists` in R to test
## whether a function or name exists in Julia or not

julia$exists("sqrt")
julia_exists("sqrt")

julia$exists("c")
julia_exists("c")

## You can use `julia$help` to get help for Julia functions

julia$help("sqrt")
julia_help("sqrt")

## Functions related to installing and using Julia packages

julia$install_package("Optim")
julia_install_package("Optim")

julia$install_package_if_needed("Optim")
julia_install_package_if_needed("Optim")

julia$installed_package("Optim")
julia_installed_package("Optim")

julia$library("Optim")
julia_library("Optim")
```

## How to Get Help?

- One way to get help for julia functions is just using `julia$help` like the following example:

```{r}
julia$help("sqrt")
julia_help("sqrt")
```

- The GitHub Pages for this repository host the documentation for the development
version of `JuliaCall`: <https://non-contradiction.github.io/JuliaCall/>.

- And you are more than welcome to contact me about `JuliaCall`
at <lch34677@gmail.com> or <cxl508@psu.edu>.

## JuliaCall for R Package Developers

If you are interested in developing an R package which is an interface for
a Julia package, `JuliaCall` is an ideal choice for that!

Basically you only need to find the Julia function or Julia module you want to have in `R`
and then just `using` the module and `call` the function.
An example is `ipoptjlr`, which can be found at <https://github.com/Non-Contradiction/ipoptjlr>.

If you have any issues in developing an `R` package using `JuliaCall`,
you may report it using the link: <https://github.com/Non-Contradiction/JuliaCall/issues/new>.
Or email me at <lch34677@gmail.com> or <cxl508@psu.edu>.

## Suggestion and Issue Reporting

`JuliaCall` is under active development now.
Any suggestion or issue reporting is welcome!
You may report it using the link: <https://github.com/Non-Contradiction/JuliaCall/issues/new>.
Or email me at <lch34677@gmail.com> or <cxl508@psu.edu>.

And if you encounter some issues which crash `R` or `RStudio`,
then you may have met segfault errors. 
I am very sorry.
And I am trying my best to remove errors like that.
It will be much appreciated if you can 

- download the source of `JuliaCall` from Github, 
- open `JuliaCall.Rproj` in your RStudio or open `R` from the directory where you download the source of `JuliaCall`,
- run `devtools::check()` to see the result of `R CMD check` for `JuliaCall` on your machine,
- and paste the result to the issue report.

